visualFields 1.0.7: Tools for Analyzing the Field of Vision in \proglang{R}

### 2025-05-17 jss-article-rnw/article.Rnw
Copyedited rest of manuscript. Compiles now.

<<preliminaries, echo=FALSE, results=hide>>=
options(prompt = "R> ", continue = "+  ", width = 70, useFancyQuotes = FALSE)
library("MASS")
@

@@

\subsection{Loading data}
The visualField package contains some example data. This dataset contains the results of 42 visual field tests of one patient (id: sample1). The patient has primary open-angle glaucoma (type: pwg).

<<>>=

str(vfpwgSunyiu24d2[, 1:10])

@@

The \texttt{glr()} function estimates a regression model for global indices. For the example series, the patient loses \texttt{r round(abs(glr(getgl(example3))$sl), 2)} dB/year, with $p < \texttt{r format(ceiling(1000 * glr(getgl(example3))$pval) / 1000, nsmall = 3)}$.

@@

plotting code from original omitted for brevity

>>>>

<<preliminaries, echo=FALSE, results=hide>>=
options(prompt = "R> ", continue = "+  ", width = 70, useFancyQuotes = FALSE)
library("MASS")
library("plotrix")
library("ggplot2")
@

@@

@@

The \texttt{glr()} function estimates a regression model for global indices. For the example series, the patient loses \texttt{getgl(example3)} dB/year, with $p < \texttt{getgl(example3)}$.

%\texttt{r round(abs(glr(getgl(example3))$sl), 2)}
%\texttt{r format(ceiling(1000 * glr(getgl(example3))$pval) / 1000, nsmall = 3)}

@@

plot_grid <- function() {
  lines(-c(10, 0.5), c(0, 0), lwd = 2, col = "lightgray")
  lines(c(0.5, 10), c(0, 0), lwd = 2, col = "lightgray")
  lines(c(0, 0), -c(10, 0.5), lwd = 2, col = "lightgray")
  lines(c(0, 0), c(0.5, 10), lwd = 2, col = "lightgray")
  lines(x = c(-0.5, 0.5), y = c(0, 0), lwd = 1.5)
  lines(x = c(0, 0), y = c(-0.5, 0.5), lwd = 1.5)
  for(r in c(2.5, 5, 7.5, 10))
    draw.circle(0, 0, r, lwd = 2, col = NA, border = "lightgray")
  text(x = 11, y = 0, "10\u00b0", adj = c(0, 0.5))
  text(x = 0, y = 11, "10\u00b0", adj = c(0.5, 0))
}

par(mfrow = c(1, 2))
plot(x = locmap$coord$x, 
     y = locmap$coord$y, 
     type = "n", 
     asp = 1,
     xlim = c(-10, 12),
     ylim = c(-10, 10),
     yaxt = 'n',
     xaxt = 'n',
     bty = 'n',
     xlab = "",
     ylab = "",
     main = "10-2 grid of test locations")
plot_grid()
points(x = locmap$coord$x, y = locmap$coord$y, bg = "white")

plot(x = locmap$coord$x, 
     y = locmap$coord$y, 
     type = "n", 
     asp = 1,
     xlim = c(-10, 12),
     ylim = c(-10, 10),
     yaxt = 'n',
     xaxt = 'n',
     bty = 'n',
     xlab = "",
     ylab = "",
     main = "Corresponding ganglion cells")
plot_grid()
points(x = gcmap$x, y = gcmap$y, pch = 21, bg = "white")
@
